Data preparation

### 2023-02-22 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Testing out joining between monthly check in data and roster data. Need to join on the current month and the following month to collect roster data.

---
title: "Data preparation"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Occupancy Patterns"
  data_folder_1: "Occupancy Data Pull"
  unique_identifier_1: !r c("employee_name","date")
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("arsenal")
devtools::install_github(repo = "GSA/oesrrr")
library(oesrrr)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(arsenal)
library(Hmisc)
```

@@

### Data from `r params$data_folder_1`

@@

```{r}
files <- 
  list.files(file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1), pattern = ".csv", full.names = TRUE)
files
```

@@

```{r}
prep_base <- files %>% 
  map_dfr(~mutate(.data = read_csv(., 
    col_types = cols(Date = col_date(format = "%m_%d_%Y"))), 
        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
      )) %>% 
  clean_names() %>% 
  distinct()
```

>>>>

---
title: "Data preparation"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Occupancy Patterns"
  data_folder_1: "Occupancy Data Pull"
  unique_identifier_1: !r c("employee_name","date")
  data_folder_2: "Rosters"
  unique_identifier_2: !r c("snapshot_date","employee_e_mail_address")
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("arsenal")
devtools::install_github(repo = "GSA/oesrrr")
library(oesrrr)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(arsenal)
library(Hmisc)
library(readxl)
```

@@

### Data files

@@

```{r}
files_1 <- 
  list.files(file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1), pattern = ".csv", full.names = TRUE)
files_1
```

Find the list of .csv files in the `r params$data_folder_2` data folder.

```{r}
files_2 <- 
  list.files(file.path(params$google_drive_home,"03. Data Collection",params$data_folder_2), pattern = ".xlsx", full.names = TRUE)
files_2
```

@@

```{r}
prep_base_1 <- files_1[1] %>% 
  map_dfr(~mutate(.data = read_csv(., 
    col_types = cols(Date = col_date(format = "%m_%d_%Y"))), 
        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
      )) %>% 
  clean_names() %>% 
  distinct() %>% 
  separate(supervisor_name,into = c("sup_last","sup_first"), sep = ",") %>% 
  mutate(
    across(
      .cols = starts_with("sup_"),
      .fns = ~word(.,1)
    )
  ) %>% 
  unite(col = "supervisor_display_name",sup_first,sup_last, sep = " ") %>% 
  rename(file_name_1 =file_name)
```

```{r}
prep_base_1_names <- names(prep_base_1)
```

Load all data files in the `r params$data_folder_2` data folder.

```{r}
prep_base_2_1 <- files_2[1] %>% 
  map_dfr(~mutate(.data = read_xlsx(path = ., 
                                    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "date", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text")), 
        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
      )) %>% 
  clean_names() %>% 
  distinct()
```

```{r}
prep_base_2_2 <- files_2[2] %>% 
  map_dfr(~mutate(.data = read_xlsx(path = ., 
                                    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "date", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text")), 
        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
      )) %>% 
  clean_names() %>% 
  distinct()
```

```{r}
prep_base_2_3 <- files_2[3] %>% 
  map_dfr(~mutate(.data = read_xlsx(path = ., 
                                    col_types = c("date", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "date", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text", 
        "text", "text", "text", "text", "text")), 
        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
      )) %>% 
  clean_names() %>% 
  distinct()
```

Joining data

```{r}
step_1 <- prep_base_1 %>% 
   left_join(prep_base_2_1,
            by = c("employee_name" = "full_name",
                   "sso" = "gsa_sso",
                   "dept_id" = "department_id",
                   "supervisor_display_name" = "supervisor_display_name"
                   )) %>% 
  # filter(rollback(date) == snapshot_date |
  #          rollforward(date) == snapshot_date) %>%
  # select(-snapshot_date, -starts_with("file_name")) %>% 
  distinct()
  # skim()
  # get_dupes(employee_e_mail_address,date)
```

```{r}
step_2 <- 
  step_1 %>% 
  filter(is.na(employee_e_mail_address)) %>% 
  select(all_of(prep_base_1_names)) %>% 
  left_join(prep_base_2_2,
            by = c("employee_name" = "full_name",
                   "sso" = "gsa_sso",
                   "dept_id" = "department_id",
                   "supervisor_display_name" = "supervisor_display_name"
                   )) %>% 
  # filter(rollback(date) == snapshot_date |
  #          rollforward(date) == snapshot_date) %>%
  # select(-snapshot_date, -starts_with("file_name")) %>% 
  distinct()
```

```{r}
step_3 <- 
  step_2 %>% 
  filter(is.na(employee_e_mail_address)) %>% 
  select(all_of(prep_base_1_names)) %>% 
  left_join(prep_base_2_3,
            by = c("employee_name" = "full_name",
                   "sso" = "gsa_sso",
                   "dept_id" = "department_id",
                   "supervisor_display_name" = "supervisor_display_name"
                   )) %>% 
  # filter(rollback(date) == snapshot_date |
  #          rollforward(date) == snapshot_date) %>%
  # select(-snapshot_date, -starts_with("file_name")) %>% 
  distinct()
```

```{r}
step_3 %>% 
  filter(!is.na(employee_e_mail_address))
```

```{r}
rollback(ymd('2022-12-01'))
rollforward(ymd('2022-12-01'))
```
